GSS Education Analysis (Working Title)

### 2023-03-07 outputs/paper/paper.qmd
update legends

---
title: "GSS Education Analysis (Working Title)"
subtitle: "GSS Education Analysis (Working Subtitle)"
author: 
  - Emily Kim
  - Huda Sahaf
  - Chloe Thierstein
thanks: "Code and data are available at: https://github.com/cthierst/gss_education_analysis.git."
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
abstract: "abstract (work in progress)"
format: pdf
number-sections: true
bibliography: references.bib
---

@@

cleaned_gss_2021 |>
  ggplot(mapping = aes(x = sex, fill = educ)) +
  geom_bar() + 
  theme_classic() +
  labs(x = "Sex",
       y = "Number",
       fill = "Highest Year Completed of Education")

@@

```
```{r}
#| echo: false
#| warning: false
#| label: fig-3
#| fig-cap: "Respondent's Sex by Highest Level of Education"

@@

cleaned_gss_2021 |>
  ggplot(mapping = aes(y = degree, fill = finrela)) +
  geom_bar() + 
  theme_classic() +
  labs(y = "Highest Level of Education",
       x = "Number",
       fill = "Rating Against Other Families")+
  scale_fill_brewer(palette = "Pastel1")+
  theme(legend.position = "bottom")
```

@@

cleaned_gss_2021 |>
  ggplot(mapping = aes(y = degree, fill = satjob)) +
  geom_bar() + 
  theme_classic() +
  labs(y = "Highest Level of Education",
       x = "Number",
       fill = "Job Satisfaction")+
  scale_fill_brewer(palette = "Pastel1")+
  theme(legend.position = "bottom")
```

@@

cleaned_gss_2021 |>
  ggplot(mapping = aes(y = degree, fill = class)) +
  geom_bar() + 
  theme_classic() +
  labs(y = "Highest Level of Education",
       x = "Number",
       fill = "Self-Ascribed Class")+
  scale_fill_brewer(palette = "Pastel1")
```

>>>>

---
title: "GSS Education Analysis (Working Title)"
subtitle: "GSS Education Analysis (Working Subtitle)"
author: 
  - Emily Kim
  - Huda Sahaf
  - Chloe Thierstein
thanks: "Code and data are available at: https://github.com/cthierst/gss_education_analysis.git"
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
abstract: "abstract (work in progress)"
format: pdf
number-sections: true
bibliography: references.bib
---

@@

cleaned_gss_2021 |>
  ggplot(mapping = aes(x = sex, fill = educ)) +
  geom_bar() + 
  theme_classic() +
  labs(x = "Sex",
       y = "Number",
       fill = "Highest Year of Education Completed")+
  theme(legend.key.size = unit(1,"line"))

@@

```{r}
#| echo: false
#| warning: false
#| label: fig-3
#| fig-cap: "Respondent's Sex by Highest Level of Education"

@@

cleaned_gss_2021 |>
  ggplot(mapping = aes(y = degree, fill = finrela)) +
  geom_bar() + 
  theme_classic() +
  labs(y = "Highest Level of Education",
       x = "Number",
       fill = "Rating Against Other Families")+
  scale_fill_brewer(palette = "Pastel1")+
  theme(legend.title = element_text(size = 6),
        legend.text= element_text(size=6))
```

@@

cleaned_gss_2021 |>
  ggplot(mapping = aes(y = degree, fill = satjob)) +
  geom_bar() + 
  theme_classic() +
  labs(y = "Highest Level of Education",
       x = "Number",
       fill = "Job Satisfaction")+
  scale_fill_brewer(palette = "Pastel1")+
  theme(legend.title = element_text(size = 6),
        legend.text= element_text(size=6))
```

@@

cleaned_gss_2021 |>
  ggplot(mapping = aes(y = degree, fill = class)) +
  geom_bar() + 
  theme_classic() +
  labs(y = "Highest Level of Education",
       x = "Number",
       fill = "Self-Ascribed Class")+
  scale_fill_brewer(palette = "Pastel1") +
  theme(legend.title = element_text(size = 8),
        legend.text= element_text(size=8))
```
